AIS

### 2023-11-21 02_AIS.Rmd
Update 02_AIS.Rmd

Required Packages
```{r setup}
library(PAMscapes)
library(tidyverse)
```

@@

>>>>

Required Packages
```{r setup}
library(PAMscapes)
library(tidyverse)
library(sf)
```

@@

# For density plots in R
```{r}
#Load allDrifts object
load("data/allDrifts.rda")

# Make allDrifts an sf object
allDrifts_sf <- allDrifts %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)
bnd <- st_bbox(allDrifts_sf)

# Make a fishnet grid over AIS points
grid <- st_make_grid(bnd, n = 30) %>%
  st_set_crs(4326)

# find which grid points intersect AIS points 
# and create an index to subset from
index <- which(lengths(st_intersects(grid, keep)) > 0)

# Subset the grid to make a fishnet
fishnet <- grid[index]
```

TAKES WAY TOO LONG
```{r}
# One way to read in files and bind
AISfiles <- list.files("D:/AIS/AIS_West", pattern = "*.csv", full.names = TRUE)
AIS_dfs <- lapply(AISfiles, read.csv) # creates list

# Row bind
AIS_allpts <- bind_rows(AIS_dfs)

# Filter broken up into many parts for easy completion! Not easy...
AIS_allpts_vLength <- AIS_allpts %>%
  filter(vesselLength >= 100)   #remove vessels under 100m in length

AIS_allpts_SOG <- AIS_allpts_vLength %>%
  filter(SOG > 0) # Filter out ships that are stopped

## Alternative way to crop (using min/max latitude of bounding box)
AIS_allpts_lat <- AIS_allpts_SOG %>%
  filter(Latitude >= min(allDrifts$Latitude))

#filter(Latitude <= max(allDrifts$Latitude)

AIS_allpts_sf <- AIS_allpts_SOG %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)

AIS_allpts_crop <- AIS_allpts_sf %>%
  st_crop(bnd)

# Write csv
write_csv(AIS_allpts_crop, file = "D:/AIS/AIS_allpts.csv")
```

# ALSO TAKES WAY TOO LONG
```{r}
# Read in AIS from one day, convert to sf, crop to allDrifts area
AISlist <- dir("D:/AIS/AIS_West", recursive=TRUE, full.names=TRUE)

# Loop through with filters
for (day in AISlist) {
  dt <- read_csv(day, show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%  #remove vessels under 100m in length
  filter(SOG > 0) %>% # Filter out ships that are stopped
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326) %>%
  st_crop(bnd)

  assign(paste0("AIS_", substr(day, 31, 35)), dt)
}
```

# one at a time works - ugh.
Filter by vessels over 100m, SOG over 2.5 knots, and increase bounding box by 0.5 on all sides
8/6 - 8/20
```{r}
# Read in one csv at a time.
AIS_08_06 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_06.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_06, file = "D:/AIS/AIS_West/AIS_08_06.rda")
#
AIS_08_07 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_07.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))
saveRDS(AIS_08_07, file = "D:/AIS/AIS_West/AIS_08_07.rda")
#
AIS_08_08 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_08.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))
saveRDS(AIS_08_08, file = "D:/AIS/AIS_West/AIS_08_08.rda")
#  
AIS_08_09 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_09.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))
saveRDS(AIS_08_09, file = "D:/AIS/AIS_West/AIS_08_09.rda")

AIS_08_10 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_10.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))
saveRDS(AIS_08_10, file = "D:/AIS/AIS_West/AIS_08_10.rda")

AIS_08_11 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_11.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_11, file = "D:/AIS/AIS_West/AIS_08_11.rda")

AIS_08_12 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_12.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_12, file = "D:/AIS/AIS_West/AIS_08_12.rda")

AIS_08_13 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_13.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))
saveRDS(AIS_08_13, file = "D:/AIS/AIS_West/AIS_08_13.rda")

AIS_08_14 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_14.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_14, file = "D:/AIS/AIS_West/AIS_08_14.rda")

AIS_08_15 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_15.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_15, file = "D:/AIS/AIS_West/AIS_08_15.rda")

AIS_08_16 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_16.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_16, file = "D:/AIS/AIS_West/AIS_08_16.rda")

AIS_08_17 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_17.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_17, file = "D:/AIS/AIS_West/AIS_08_17.rda")

AIS_08_18 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_18.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_18, file = "D:/AIS/AIS_West/AIS_08_18.rda")

AIS_08_19 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_19.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_19, file = "D:/AIS/AIS_West/AIS_08_19.rda")

AIS_08_20 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_20.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_20, file = "D:/AIS/AIS_West/AIS_08_20.rda")

8/21 - 8/31
```{r}
AIS_08_21 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_21.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_21, file = "D:/AIS/AIS_West/AIS_08_21.rda")

AIS_08_22 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_22.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_22, file = "D:/AIS/AIS_West/AIS_08_22.rda")

AIS_08_23 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_23.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_23, file = "D:/AIS/AIS_West/AIS_08_23.rda")

AIS_08_24 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_24.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_24, file = "D:/AIS/AIS_West/AIS_08_24.rda")

AIS_08_25 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_25.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_25, file = "D:/AIS/AIS_West/AIS_08_25.rda")

AIS_08_26 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_26.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_26, file = "D:/AIS/AIS_West/AIS_08_26.rda")

AIS_08_27 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_27.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_27, file = "D:/AIS/AIS_West/AIS_08_27.rda")

AIS_08_28 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_28.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_28, file = "D:/AIS/AIS_West/AIS_08_28.rda")

AIS_08_29 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_29.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_29, file = "D:/AIS/AIS_West/AIS_08_29.rda")

AIS_08_30 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_30.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_30, file = "D:/AIS/AIS_West/AIS_08_30.rda")

AIS_08_31 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_08_31.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_08_31, file = "D:/AIS/AIS_West/AIS_08_31.rda")
```

9/1 - 9/15
```{r}
AIS_09_01 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_01.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_01, file = "D:/AIS/AIS_West/AIS_09_01.rda")

AIS_09_02 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_02.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_02, file = "D:/AIS/AIS_West/AIS_09_02.rda")

AIS_09_03 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_03.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_03, file = "D:/AIS/AIS_West/AIS_09_03.rda")

AIS_09_04 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_04.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_04, file = "D:/AIS/AIS_West/AIS_09_04.rda")

AIS_09_05 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_05.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_05, file = "D:/AIS/AIS_West/AIS_09_05.rda")

AIS_09_06 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_06.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_06, file = "D:/AIS/AIS_West/AIS_09_06.rda")

AIS_09_07 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_07.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_07, file = "D:/AIS/AIS_West/AIS_09_07.rda")

AIS_09_08 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_08.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_08, file = "D:/AIS/AIS_West/AIS_09_08.rda")

AIS_09_09 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_09.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_09, file = "D:/AIS/AIS_West/AIS_09_09.rda")

AIS_09_10 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_10.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_10, file = "D:/AIS/AIS_West/AIS_09_10.rda")

AIS_09_11 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_11.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_11, file = "D:/AIS/AIS_West/AIS_09_11.rda")

AIS_09_12 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_12.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_12, file = "D:/AIS/AIS_West/AIS_09_12.rda")

AIS_09_13 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_13.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_13, file = "D:/AIS/AIS_West/AIS_09_13.rda")

AIS_09_14 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_14.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_14, file = "D:/AIS/AIS_West/AIS_09_14.rda")

AIS_09_15 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_15.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_15, file = "D:/AIS/AIS_West/AIS_09_15.rda")

9/16 - 9/30
```{r}
AIS_09_16 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_16.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_16, file = "D:/AIS/AIS_West/AIS_09_16.rda")

AIS_09_17 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_17.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_17, file = "D:/AIS/AIS_West/AIS_09_17.rda")

AIS_09_18 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_18.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_18, file = "D:/AIS/AIS_West/AIS_09_18.rda")

AIS_09_19 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_19.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_19, file = "D:/AIS/AIS_West/AIS_09_19.rda")

AIS_09_20 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_20.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_20, file = "D:/AIS/AIS_West/AIS_09_20.rda")

AIS_09_21 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_21.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_21, file = "D:/AIS/AIS_West/AIS_09_21.rda")

AIS_09_22 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_22.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_22, file = "D:/AIS/AIS_West/AIS_09_22.rda")

AIS_09_23 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_23.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_23, file = "D:/AIS/AIS_West/AIS_09_23.rda")

AIS_09_24 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_24.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_24, file = "D:/AIS/AIS_West/AIS_09_24.rda")

AIS_09_25 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_25.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_25, file = "D:/AIS/AIS_West/AIS_09_25.rda")

AIS_09_26 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_26.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_26, file = "D:/AIS/AIS_West/AIS_09_26.rda")

AIS_09_27 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_27.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_27, file = "D:/AIS/AIS_West/AIS_09_27.rda")

AIS_09_28 <- read_csv("D:/AIS/AIS_West/West_AIS_2018_09_28.csv", 
                      show_col_types = FALSE) %>%
  filter(vesselLength >= 100) %>%
  filter(SOG > 2.5) %>%
  filter(Latitude >= min(allDrifts$Latitude - 0.5) & Latitude <= max(allDrifts$Latitude + 0.5)) %>%
  filter(Longitude >= min(allDrifts$Longitude - 0.5) & Longitude <= max(allDrifts$Longitude + 0.5))

saveRDS(AIS_09_28, file = "D:/AIS/AIS_West/AIS_09_28.rda")
